---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
  [![Travis build status](https://travis-ci.com/muschellij2/mFilter.svg?branch=master)](https://travis-ci.com/muschellij2/mFilter)
  [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/muschellij2/mFilter?branch=master&svg=true)](https://ci.appveyor.com/project/muschellij2/mFilter)
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mFilter

The package implements several time series filters useful
        for smoothing and extracting trend and cyclical components of a
        time series. The routines are commonly used in economics and
        finance, however they should also be interest to other areas.
        Currently, Christiano-Fitzgerald, Baxter-King,
        Hodrick-Prescott, Butterworth, and trigonometric regression
        filters are included in the package.

## Installation

You can install the released version of mFilter from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("mFilter")
```

## Example

This is a basic example which shows you how to do Butterworth filtering:

```{r }
library(mFilter)
data(unemp)
unemp.bw <- bwfilter(unemp)
plot(unemp.bw)
unemp.bw1 <- bwfilter(unemp, drift=TRUE)
unemp.bw2 <- bwfilter(unemp, freq=8,drift=TRUE)
unemp.bw3 <- bwfilter(unemp, freq=10, nfix=3, drift=TRUE)
unemp.bw4 <- bwfilter(unemp, freq=10, nfix=4, drift=TRUE)
```

```{r}
par(mfrow=c(2,1),mar=c(3,3,2,1),cex=.8)
plot(unemp.bw1$x,
     main="Butterworth filter of unemployment: Trend, 
     drift=TRUE",col=1, ylab="")
lines(unemp.bw1$trend,col=2)
lines(unemp.bw2$trend,col=3)
lines(unemp.bw3$trend,col=4)
lines(unemp.bw4$trend,col=5)
legend("topleft",legend=c("series", "freq=10, nfix=2", 
       "freq=8, nfix=2", "freq=10, nfix=3", "freq=10, nfix=4"), 
       col=1:5, lty=rep(1,5), ncol=1)
```
```{r ex3}
plot(unemp.bw1$cycle,
     main="Butterworth filter of unemployment: Cycle,drift=TRUE", 
     col=2, ylab="", ylim=range(unemp.bw3$cycle,na.rm=TRUE))
lines(unemp.bw2$cycle,col=3)
lines(unemp.bw3$cycle,col=4)
lines(unemp.bw4$cycle,col=5)

```
